COSC-373 Final Report: Bitcoin

### 2022-05-19 paper/paper.tex
Changed citations. Need to fix formatting.

\section{Conclusion}
We discussed in this report the fundamental structure of Bitcoin and how it solves the doublesepnding problem. Other aspects of Bitcoin include incentivizing miners, reclaiming unnecessary disk space, and combining and splitting values in a transaction. You can read more about these topics in the original Bitcoin paper [Nakamoto, 2008]. Further work aims to increase the rate of transactions  by establishing micropayment channels between two parties outside the blockchain network (https://tik-old.ee.ethz.ch/file/716b955c130e6c703fac336ea17b1670/duplex-micropayment-channels.pdf). Lastly, the introduction of a decentralized system for financial transactions by Bitcoin led to a number of other blockchain-based cryptocurrencies such as Ethereum. You can read about the structure of Ethereum from Ferretti and D’Angelo’s 2019 paper (https://arxiv.org/pdf/1908.11808.pdf).

>>>>

\section{Conclusion}
We discussed in this report the fundamental structure of Bitcoin and how it solves the doublesepnding problem. Other aspects of Bitcoin include incentivizing miners, reclaiming unnecessary disk space, and combining and splitting values in a transaction. You can read more about these topics in the original Bitcoin paper ~\citep{Nakamoto08}. Further work aims to increase the rate of transactions  by establishing micropayment channels between two parties outside the blockchain network ~\citep{Decker15}. Lastly, the introduction of a decentralized system for financial transactions by Bitcoin led to a number of other blockchain-based cryptocurrencies such as Ethereum. You can read about the structure of Ethereum from Ferretti and D’Angelo’s paper ~\citep{Ferretti19}.
